The Concurrent Calculi Formalisation Benchmark

### 2024-02-20 short-paper/short-paper.tex
references for hammer, others less revant removed

Additionally, many proof assistants lack support for the proof principles required to easily work with scope extrusion, \ie, induction principles on functions to work with HOAS encodings.
Some proof assistants such as Abella~\cite{Baelde2014} support HOAS natively, but working with open terms as required to encode scope extrusion in these systems is generally very challenging~\cite{Momigliano2012}.

@@

Also, one could easily design a challenge that goes beyond our
coinduction challenge, by exploring different notions of process equivalence.
%
Coinduction may also play a relevant role in supporting recursive processes and
session types. Indeed, it is often the case that session type systems (and
logics) with recursive session types (and propositions) are naturally expressed
in \emph{infinitary form} by interpreting their typing (and proof) rules
coinductively~\cite{BaeldeDoumaneSaurin16,DerakhshanPfenning22,HornePadovani23}.

Finally, another interesting avenue to explore would be to take
advantage of certain proof assistant features: for example, extracting
certified implementations (as in \cite{Castro-Perez2021}) or exploiting
proof automation, such as the one offered by the \emph{Hammer}
approach.\todo{citation here?}

>>>>

Additionally, many proof assistants lack support for the proof principles required to easily work with scope extrusion, \ie, induction principles on functions to work with HOAS encodings.
Some proof assistants such as Abella  support HOAS natively, but working with open terms as required to encode scope extrusion in these systems is generally very challenging.

@@

Also, one could easily design a challenge that goes beyond our
coinduction challenge, by exploring different notions of process equivalence.
%
Coinduction may also play a relevant role in supporting recursive processes and
session types. Indeed, it is often the case that session type systems (and
logics) with recursive session types (and propositions) are naturally expressed
in \emph{infinitary form} by interpreting their typing (and proof) rules
coinductively~\cite{%BaeldeDoumaneSaurin16,
DerakhshanPfenning22,HornePadovani23}.

Finally, another interesting avenue to explore would be to take
advantage of certain proof assistant features: for example, extracting
certified implementations (as in \cite{Castro-Perez2021}) or exploiting
proof automation, such as the one offered by the \emph{Hammer}
protocol~\cite{BohmeN10,CzajkaK18}.
